---
title: "CS6313.002 Statistical Project 1"
author: "Ruolan Zeng(rxz171630), Vineet Vilas Amonkar(vva180000), Aakash Kamlesh Punjabi(
akp170430)"
date: "Oct 24th 2018"
output: html_document
---

## Token Selection

The token we use: networkstorjTX.txt

## Preprocessing

**Load TokenData:**

```{r}
tokenData <- read.delim("networkstorjTX.txt", header = FALSE, sep = " ")
tokenFrame<- as.data.frame(tokenData)
colnames(tokenFrame) <- c("fromNodeID","toNodeID","unixTime","tokenAmount")
head(tokenFrame)
```

**Find Outliers:**

```{r}
TotalSupply <- 424999998
Decimals <- 10^8
OutlierValue <- TotalSupply*Decimals
Outlierdata <- tokenFrame[ which(tokenFrame$tokenAmount > OutlierValue),]
head(Outlierdata)
```

**Total Number Of Outliers:**

```{r}
message("Total number of outliers: ", length(Outlierdata$tokenAmount))
```

**How Many Users Are Included In Outliers Transactions:**

```{r}
users <- c(Outlierdata$fromNodeID,Outlierdata$toNodeID)
uniqueUsers<- unique(users)
message(length(uniqueUsers), " users are includednin outliers transactions")

```

**Remove Outliers**
```{r}
WithoutOutlierdata <- tokenFrame[ which(tokenFrame$tokenAmount < OutlierValue),]
```

## Q1
## Find Distribution -- Buys

```{r}
frequencyTable <- table(WithoutOutlierdata[2])
freq<- as.data.frame(frequencyTable)
colnames(freq) <- c("buyerID","frequency")
head(freq)
FrequencyBuyers = table(freq$frequency)
freqNoBuys = as.data.frame(FrequencyBuyers)
colnames(freqNoBuys) <- c("NoBuys","freqNoBuys")
head(freqNoBuys)

```


```{r}
barplot(freqNoBuys$freqNoBuys,names.arg = freqNoBuys$NoBuys,ylab = "frequencyNoBuys", xlab = "NoBuys", xlim = c(0,20),ylim = c(0,140000))
```

## Fit Distribution -- Buys

```{r}
message("mean of frequency of number of buys is ", mean(freqNoBuys$freqNoBuys))
message("variance of frequency of number of buys is ", sd(freqNoBuys$freqNoBuys)^2)
message("standard deviation of frequency of number of buys is ", sd(freqNoBuys$freqNoBuys))
```

**1. Poisson Distribution**
```{r}
library(fitdistrplus)
fit <- fitdist(freqNoBuys$freqNoBuys, "pois", method="mle")
fit
```

```{r}
plot(fit)
```

**2. Weibull Distribution**
```{r}
fit2 <- fitdist(freqNoBuys$freqNoBuys, "weibull",method = "mle")
fit2
```

```{r}
plot(fit2)
```

**3. Exponential Distribution**
```{r}
fit3 <- fitdist(freqNoBuys$freqNoBuys, "exp",method = "mme")
fit3
```

```{r}
plot(fit3)
```

**4. Geometric Distribution**
```{r}
fit4 <- fitdist(freqNoBuys$freqNoBuys, "geom",method = "mme")
fit4
```
```{r}
plot(fit4)
```

**5. Normal Distribution**
```{r}
message("mean of frequency of number of buys is ", mean(freqNoBuys$freqNoBuys))
message("standard deviation of frequency of number of buys is ", sd(freqNoBuys$freqNoBuys))
fit5 <- fitdist(freqNoBuys$freqNoBuys, "norm")
fit5
```

```{r}
plot(fit5)
```

## Find Distribution -- Sells

```{r}
frequencyTable <- table(WithoutOutlierdata[1])
freq<- as.data.frame(frequencyTable)
colnames(freq) <- c("sellerID","frequency")
head(freq)
FrequencySellers = table(freq$frequency)
freqNoSells = as.data.frame(FrequencySellers)
colnames(freqNoSells) <- c("NoSells","freqNoSells")
head(freqNoSells)
```

```{r}
barplot(freqNoSells$freqNoSells,names.arg = freqNoSells$NoSells,ylab = "freqNoSells", xlab = "NoSells", xlim = c(0,20),ylim = c(0,50000))
```

## Fit Distribution -- Sells

```{r}
message("mean of frequency of number of sells is ", mean(freqNoSells$freqNoSells))
message("variance of frequency of number of buys is ", sd(freqNoSells$freqNoSells)^2)
message("standard deviation of frequency of number of buys is ", sd(freqNoSells$freqNoSells))
```

**1. Poisson Distribution**

```{r}
library(fitdistrplus)
fitSells <- fitdist(freqNoSells$freqNoSells, "pois", method="mle")
fitSells
```

From above, we observe that mean is equal to lambda, hence, distribution is poisson distribution.

```{r}
plot(fitSells)
```

**2. Weibull Distribution**
```{r}
fitSells2 <- fitdist(freqNoSells$freqNoSells, "weibull",method = "mle")
fitSells2
```

```{r}
plot(fitSells2)
```

**3. Exponential Distribution**
```{r}
fitSells3 <- fitdist(freqNoSells$freqNoSells, "exp",method = "mme")
fitSells3
```

```{r}
plot(fitSells3)
```

**4. Geometric Distribution**
```{r}
fitSells4 <- fitdist(freqNoSells$freqNoSells, "geom",method = "mme")
fitSells4
```
```{r}
plot(fitSells4)
```

**5. Normal Distribution**
```{r}
message("mean of frequency of number of sells is ", mean(freqNoSells$freqNoSells))
message("standard deviation of frequency of number of buys is ", sd(freqNoSells$freqNoSells))
fitSells5 <- fitdist(freqNoSells$freqNoSells, "norm")
fitSells5
```

```{r}
plot(fitSells5)
```

##Conclusion
After compare with parameters and graphs of different distributions, we can find:

The estimate parameters of Normal Distribution are very close to the parameters of our token data, but the graphs don't fit well. 
The graphs of Poisson Distribution and Weibull Distribution both fit our token data well, but for the parameters, the mean(buys:1331.66, sells:499.26) is not equal to variance(buys:133341824.3, sells:17815729.69), so it should not be Poisson Distribution.

Hence, we finally conclude that **Weibull Distribution** fit our distribution best.
